Supplementary Material for 'The complex network of trophic interactions in

### 2023-05-08 MS_ToSubmit/SupMaterial.Rmd
2nd version w/ coauthors suggs

---
title: "Supplementary material for 'The complex network of trophic interactions in a subAntarctic Marine Protected Area'"
author: "Tomás I. Marina, Irene R. Schloss, Luciana Riccialdelli, To be continued"
output: pdf_document
bibliography: "AMPBancoBurdwood.bib"
---

@@

The following figure and tables summarize the data we used to build the network of trophic (predator-prey) interactions for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
Figure 1 resumes the type and number of references reviewed. Table 1 is the complete list of trophic interactions and references that confirm each of them. Table 2 is the species list with details on trophic species cases (aggregated taxa).

@@

# Load data
load("../data/cleaned-data_apr23.rda")

@@

# Load data
load("../data/cleaned-data_apr23.rda")
load("../data/foodweb-data_apr23.rda")

@@

Figure 2 shows the species' topological roles in the food web graph. Species, represented by circles, are coloured by role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green). Network connector = 5 species; module connector = 35 species; module hub = 7 species; and module specialist = 332 species.

```{r toprole_graph, echo=FALSE, fig.width = 20, fig.height=20, fig.cap="Graph of the food web showing species coloured by topological role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green)."}

@@

# Load data
load("../results/summary_results_apr23.rda")

>>>>

---
title: "Supplementary Material for 'The complex network of trophic interactions in
  a subAntarctic oceanic Marine Protected Area'"
author:
  - Tomás I. Marina
  - Irene R. Schloss
  - Luciana Riccialdelli
  - Fabiana L. Capitanio
  - Sergio M. Delpiani
  - Juan Martín Díaz de Astarloa
  - Cintia Fraysse
  - Gustavo A. Lovrich
  - Andrea Raya Rey
  - Mariela L. Spinelli
  - Diego Urteaga
  - Marcos Tatián
  - Virginia A. García Alonso
  - Claudia C. Boy
  - Daniel O. Bruno
bibliography: AMPBancoBurdwood.bib
output: pdf_document
---

@@

The following figure and tables summarise the data we used to build the network of trophic (predator-prey) interactions for the Marine Protected Area Namuncurá - Banco Burdwood I ecosystem.
Figure 1 resumes the type and number of references reviewed. Table 1 is the complete list of trophic interactions and references that confirm each of them. Table 2 is the species list with details on trophic species cases (aggregated taxa).

@@

# Load data
load("../data/cleaned-data_may23.rda")

@@

# Load data
load("../data/cleaned-data_may23.rda")
load("../data/foodweb-data_may23.rda")

@@

Figure 2 shows the species' topological roles in the food web graph. Species, represented by circles, are coloured by role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green). Network connector = 4 species; module connector = 37 species; module hub = 8 species; and module specialist = 326 species.

```{r toprole_graph, echo=FALSE, fig.width = 20, fig.height=20, fig.cap="Graph of the food web showing species coloured by topological role: network connector (dark purple), module connector (light pink), module hub (light green), and module specialist (dark green). Circle diameter is relative to the number of interactions."}

@@

# Load data
load("../results/summary_results_may23.rda")
